%Copyright 2014 Jean-Philippe Eisenbarth
%This program is free software: you can 
%redistribute it and/or modify it under the terms of the GNU General Public 
%License as published by the Free Software Foundation, either version 3 of the 
%License, or (at your option) any later version.
%This program is distributed in the hope that it will be useful,but WITHOUT ANY 
%WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A 
%PARTICULAR PURPOSE. See the GNU General Public License for more details.
%You should have received a copy of the GNU General Public License along with 
%this program.  If not, see <http://www.gnu.org/licenses/>.

%Based on the code of Yiannis Lazarides
%http://tex.stackexchange.com/questions/42602/software-requirements-specification-with-latex
%http://tex.stackexchange.com/users/963/yiannis-lazarides
%Also based on the template of Karl E. Wiegers
%http://www.se.rit.edu/~emad/teaching/slides/srs_template_sep14.pdf
%http://karlwiegers.com
\documentclass{scrreprt}
\makeatletter
\newcommand{\getCurrentSectionNumber}{%
  \ifnum\c@section=0 %
  \thechapter
  \else
  \ifnum\c@subsection=0 %
  \thesection
  \else
  \ifnum\c@subsubsection=0 %
  \thesubsection
  \else
  \thesubsubsection
  \fi
  \fi
  \fi
}

\usepackage{listings}
\usepackage{underscore}
\usepackage[bookmarks=true]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{nameref}
\hypersetup{
    bookmarks=false,    % show bookmarks bar?
    pdftitle={Software Requirement Specification},    % title
    pdfauthor={Jean-Philippe Eisenbarth},                     % author
    pdfsubject={TeX and LaTeX},                        % subject of the document
    pdfkeywords={TeX, LaTeX, graphics, images}, % list of keywords
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=blue,       % color of internal links
    citecolor=black,       % color of links to bibliography
    filecolor=black,        % color of file links
    urlcolor=purple,        % color of external links
    linktoc=page            % only page is linked
}%
\def\myversion{1.0 }
\date{}
%\title{%

%}
\usepackage{hyperref}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{document}

\begin{flushright}
    \rule{16cm}{5pt}\vskip1cm
    \begin{bfseries}
        \Huge{SOFTWARE REQUIREMENTS\\ SPECIFICATION}\\
        \vspace{1.9cm}
        for\\
        \vspace{1.9cm}
        kertasrapi v1.0\\
        \vspace{1.9cm}
        \LARGE{Version \myversion approved}\\
        \vspace{1.9cm}
        Prepared by Sandi Wibowo\\
        \vspace{1.9cm}
        Kertas Rapi\\
        \vspace{1.9cm}
        \today\\
    \end{bfseries}
\end{flushright}

\tableofcontents


\chapter*{Revision History}

\begin{center}
    \begin{tabular}{|c|c|c|c|}
        \hline
	    Name & Date & Reason For Changes & Version\\
        \hline
	    21 & 22 & 23 & 24\\
        \hline
	    31 & 32 & 33 & 34\\
        \hline
    \end{tabular}
\end{center}

\chapter{Introduction}

\section{Purpose}
The purpose of this document is to give a guideline, to state a set of description, and to serve as initial direction of a production cycle. It will state a set of requirements that must be implemented for a release v1.0. The nature of agile methodology allows the modfication of this document as we progress. 

The stage of the project is not just an idea but the technology has been implenented and serve as a first MVP (minimum viable product). The demo of this product is presented at http://demo.kertasrapi.com. It will be helpful to understand the specifications if one has tried the demo before. 

\section{Document Definition}
\begin{itemize}
\item Demo: http://demo.kertasrapi.com
\item kertasrapi: the name of this application is kertasrapi. This project is to build web application and referred as kertasrapi. 
\item Shareholder(s): any interest party that has authority to set direction  of the project.
\item User(s): the consumer of this application. Teacher, tutor, lecturer, or any educator are the potential users.
\item Problem: A single material in  homework, assignment or exam
\item p-cart: A cart containing problems that has been selected by user.
\end{itemize}

\section{Intended Audience and Reading Suggestions}
\begin{enumerate}
\item Shareholder  \\
  Verbal description gives general idea of the project. Moreover, This written document is intended to give more thorough and transparant description of it. Therefore, shareholder or any interest party can evaluate the potential, the feasibility, or the fit of shareholder's interest and vision.  
\item System architech \\
 Following this guideline serves as direction of how to architect the corresponding technology. System architech can create system design document based on the defined specification.
\item Tester  \\
    Specification serve as a direction of what test cases should be included. A set of test cases must be generated to satisfy the requirement. 
\end{enumerate}

This document has three chapters and a appendixes. The second one provide descriptive of working functionality and the interaction with other system. The third chapter describes a set of requirements to be satisfied as features for release v1.0. The appendixes include a discussion about posibilities implementing the technology on different field other than education.  

\section{Project Scope}
This project is to build web application that has function as assignment management system. The goal is to provide convenient ways to educator to produce documents for assignment/exam/handout. 

The idea is to provide a service platform for educators. The platform allow educator to select which assignment they want to include then the platform will generate a clean neat document for that assignment. Go to http://demo.kertasrapi.com to try the working system.

\section{References}
\begin{enumerate}
    \item http://demo.kertasrapi.com
\end{enumerate}

\chapter{Overall Description}

\section{Product Perspective}
This product is a stand alone web application that can be accessed through web browser which is connected to internet. The product is to provide services of automatic document generator. Users of this product only concern about content and its sequence, the output document of is handled by this product. For the moment, the focus of the product is to automated the document generation of assgnment or exam. Mainly the user of kertasrapi is members of school or any educational institution where preparation of exam/assignment is a part of recurring activity.    

\section{Product Functions}
The main functionality of kertasrapi is to take over the responsbility of gnerating document from user to the system . Kertasrapi will provide a collection of problems and solution in school level. User can select which problem to be assembled. Afterthat, a user select which template to be used. The final result is a well ordered document generated by kertasrapi ready to be handed out to students. The step is illustrated in figur

The system consist of three components. Those are front end as web interface, backend as content management, and API as document generator. Front end is client/browser web application that rely on java script. Backend consist of API and database to store data such as user profile, problem solution, label, etc. The API is the heart of this product and the function is to generate realtime document based on user request. 

The functionality of a user can upload their own problem-solution will be provided for the release v2.0. For the release v1.0, user can send or email the content to kertasrapi's team and our team is the one who will upload the content to the system. The reason of that because by kertasrapi's team gather data during the process of uploading the content. The data is important to determine how to create compelling text editor customized the education institution. The process for v1.0 is illustrated in figure


\section{User Classes and Characteristics}
School or education institution is the main client of kertasrapi. The actual users will be the members of education institution such as teacher, tutor, or lecturer. The users can accss the web only if their school has estabilished relation with kertasrapi(e.g pay subscription fee). 

Any user or teacher can register to kertasrapi but they will not have access to any features. Once a user establish relation to kertasrapi then kertasrapi will send secret code to him/her. He/She can now distribute the secret code to all members of school. Other member of school can access the web by inserting the secret code for their own school.

Users can login either using email or cellphone number. The login cellphone is provided to give better flexibility given that not all teach are active email user. The form to change their email or cellphone will be provided

\section{Operating Environment}
This web application works on web browser. Any operating system that has web browser installed can be used to run this application. Any devices that are able to run web browser can be used to run this application

\section{Design and Implementation Constraints}
Proper internet connection is the constraint to use this app. The internet connection should be  able to have enough speed to transfer pdf document. A web browser is required to access this document. 
https://www.w3.org/TR/2012/REC-WOFF-20121213/

\section{User Documentation}
A cookbook-like document showing how to use the application will be provided and can be downloaded in pdf from user support page. Customer support will be provided using email, call, or letter.

\section{Assumptions and Dependencies}
The assumption here is the web browser must have compatibility that follow web font standard. A web browser that is released after 2012 can handle this app.


\chapter{External Interface Requirements}

\section{User Interfaces}
The items below are general description about the available web interface to user:
\begin{itemize}
    \item An interface to register.
        This page cantains item to insert email or cellphone number (for those who doesn't use emai) and password. Verification will be send to their email or SMS that the register has been successful.
    \item An interface to login page.
        This page contains fields to login using email/cell-number and password.
    \item An interface to user management.
        This page contains information about user. It shows current information of their email/cellphone number. There is a field to change their password. Another important field is to add secondary email or cellphone number.
    \item An interface to insert secret code.
        This page contains a field to insert their secret code. 
    \item An interface to access the collection of problems.
        This page(s) contain all available problems (and with their solution). The illustration is given in demo. 
    \item An interface or a tool to select, search and put a problem to p-cart. 
        This page(s) contain tools to retrieve information most relevant to the user. 
    \item An interface or tool to add information on p-cart.
        This page(s) contain tool where user can add information before the document is generated. Any information that is given to template can be inserted here.  
    \item An interface to show information about the company, contact support, and instruction how to upload problems to the app.
\end{itemize}

\section{Hardware Interfaces}
Modern computer or smartphone with web browser installed should be able to run the app. An interface to select item in web app is required, those interface can be mouse, keyboard, touch screen, touch pad, etc.  


\section{Software Interfaces}
Database is stored in backend component. There is another component/service which connect backend to API.The service will read data from backend/database then send it to API processer and return the document back to backend. The API will concern only about processing and will not store any data.   

\section{Communications Interfaces}
Web browser communicate through our API using standard HTTP 1.1. The request of a user selecting particular items is represented by HTTP 1.1 request to kertasprapi's API. 

\chapter{System Features}
This chaper include the requirment for this app

\section{User management}

\subsection{FRv1.\arabic{section}.\arabic{subsection}}
\label{fr:register}
\begin{center}
    \begin{tabular}{|l|L{9cm}|}
        \hline
         TITLE& Register\\ \hline
         DESCRIPTION& User can register using email or cellphone number   \\ \hline
         DEPENDENCY& None \\ \hline
    \end{tabular}
\end{center}

\subsection{FRv1.\arabic{section}.\arabic{subsection}}
\label{fr:login}
\begin{center}
    \begin{tabular}{|l|L{9cm}|}
        \hline
         TITLE& Login\\ \hline
         DESCRIPTION& User can login using email or cellphone number and password   \\ \hline
         DEPENDENCY& \ref{fr:register}\\ \hline
    \end{tabular}
\end{center}

\subsection{FRv1.\arabic{section}.\arabic{subsection}}
\label{fr:changeid}
\begin{center}
    \begin{tabular}{|l|L{9cm}|}
        \hline
         TITLE& Change id\\ \hline
         DESCRIPTION& After user register, they can change their primary id (Either email or cellphone)\\ \hline
         DEPENDENCY& \ref{fr:register} \ref{fr:login}\\ \hline
    \end{tabular}
\end{center}


\subsection{FRv1.\arabic{section}.\arabic{subsection}}
\label{fr:payment}
\begin{center}
    \begin{tabular}{|l|L{9cm}|}
        \hline
         TITLE& Payment\\ \hline
         DESCRIPTION& To accept payment as a part of premium service \\ \hline
         DEPENDENCY& \ref{fr:register} \ref{fr:login}\\ \hline
    \end{tabular}
\end{center}

\section{Item management}

\subsection{FRv1.\arabic{section}.\arabic{subsection}}
\label{fr:listp}
\begin{center}
    \begin{tabular}{|l|L{9cm}|}
        \hline
         TITLE& List problem\\ \hline
         DESCRIPTION& User can go to problem's page and list all problem they can access \\ \hline
         DEPENDENCY& \ref{fr:register} \ref{fr:login}\\ \hline
    \end{tabular}
\end{center}

\subsection{FRv1.\arabic{section}.\arabic{subsection}}
\label{fr:sortp}
\begin{center}
    \begin{tabular}{|l|L{9cm}|}
        \hline
         TITLE& Sort by label\\ \hline
         DESCRIPTION& User can filter out problem based on their labels \\ \hline
         DEPENDENCY& \ref{fr:register} \ref{fr:login}\\ \hline
    \end{tabular}
\end{center}

\subsection{FRv1.\arabic{section}.\arabic{subsection}}
\label{fr:sortp}
\begin{center}
    \begin{tabular}{|l|L{9cm}|}
        \hline
         TITLE& Search item\\ \hline
         DESCRIPTION& User can search the problem which are most relevant to them\\ \hline
         DEPENDENCY& \ref{fr:register} \ref{fr:login}\\ \hline
    \end{tabular}
\end{center}

\subsection{FRv1.\arabic{section}.\arabic{subsection}}
\label{fr:putcart}
\begin{center}
    \begin{tabular}{|l|L{9cm}|}
        \hline
         TITLE& Put to p-cart\\ \hline
         DESCRIPTION& User can add problem to temporary container before generating document \\ \hline
         DEPENDENCY& \ref{fr:register} \ref{fr:login}\\ \hline
    \end{tabular}
\end{center}

\subsection{FRv1.\arabic{section}.\arabic{subsection}}
\label{fr:remcart}
\begin{center}
    \begin{tabular}{|l|L{9cm}|}
        \hline
         TITLE& Remove from p-cart\\ \hline
         DESCRIPTION& User can remove the items/problem from temporary container \\ \hline
         DEPENDENCY& \ref{fr:register} \ref{fr:login}\\ \hline
    \end{tabular}
\end{center}

\subsection{FRv1.\arabic{section}.\arabic{subsection}}
\label{fr:addinfo}
\begin{center}
    \begin{tabular}{|l|L{9cm}|}
        \hline
         TITLE& Add information to template\\ \hline
         DESCRIPTION& User can add information to template before generating document\\ \hline
         DEPENDENCY& \ref{fr:register} \ref{fr:login}\\ \hline
    \end{tabular}
\end{center}

\subsection{FRv1.\arabic{section}.\arabic{subsection}}
\label{fr:genpdf}
\begin{center}
    \begin{tabular}{|l|L{9cm}|}
        \hline
         TITLE& Generate document\\ \hline
         DESCRIPTION& User can generate pdf document based on p-cart and information in container    \\ \hline
         DEPENDENCY& \ref{fr:register} \ref{fr:login}\\ \hline
    \end{tabular}
\end{center}

\subsection{FRv1.\arabic{section}.\arabic{subsection}}
\label{fr:downloadpdf}
\begin{center}
    \begin{tabular}{|l|L{9cm}|}
        \hline
         TITLE& Download document\\ \hline
         DESCRIPTION& After the process of generating is finished, User can download it \\ \hline
         DEPENDENCY& \ref{fr:register} \ref{fr:login}\\ \hline
    \end{tabular}
\end{center}

\section{Nonfunctional Requirements}

\subsection{Consistency Requirements}
The standard of consistency become vital because of multiple device (interface) can be used to access the web app. There are three possible category of it. First is the hardware or device that they are using. The second layer is the operating system of it. The last layer is the web browser that is used to access the web app. The quality of document should be independent of those layers. Any users who access from any device, operating system, and web browser must receive the exact identical document as per their request.   

The consistency in this manner is also defined as a constraint to be interoperable. If the quality of document generated is the same quality of printed media (e.g. book) then the emphasize is to focus on technology which has the quality of printed media. The quality of the output document should be defined by that technology, not with the interface of the technology. 

\section{Reliability Requirements}
All server which host web application has limit to what number of request they can handle over a given time. The reliability requirement indicate that the server or the infrastructure must scale horizontally to adapt to the demand of users request. Other part of reliability is to detect a failure in a process and be able to handle them under a given circumstances.   

\section{Extensibility Requirements}
The core of this web application is the technology to generate high quality document that has standard of printed media. Such technology doesn't limit them self just for education purpose. It open the application across different field where generation of printed media is needed. The requirement of extensibility impose that the API to generate document open them self to any document without limitiation to education field.  


\section{Appendix}
The demo (http://demo.kertasrapi.com) showcase the capability of the technology. The field of scientific publishing has been using the similar type of technology. Important to note, the strong point of this technology is not just to assemble document but to typeset it, Furthermore, it allows separation between the content provided and the designer. The main reason choosing technology from scientific publising is to have reliable, consistent, and extensibible technology to generate document in realtime.   

Document generator and its management is open problem because there are different customization for different fields. However, the technology to generate document in realtime is field-agnostic. The possibility to implement this technology in different field is still open widely. In conclusion, the direction of this project may be shifted if one can find compelling use case for this technology. 
\end{document}
